Product plots

### 2011-06-23 prodplots-infovis.tex
Fix references

The product plots framework is heavily influenced by the work of WIlkinson \citep{wilkinson:1999, wilkinson:2005}, who introduced the set product operator to map hierarchical data to a two-dimensional framework.  Wilkinson restricts (??? not quite sure - need to lookit up) the use to standard mosaicplots as defined by \citet{hartigan:1981}, which could easily be extended, however the product plots framework additionally introduces the concept of conditioning on variables.

@@

The framework of  Polaris  \cite{stolte:2002} relies heavily on a tabular or cubic format in rendering hierarchical graphics, which makes these charts essentially a three dimensional extension of the trellis framework \citep{cleveland:1994, cleveland:1996}:  in the product plots framework, this approach is captured by conditioning on the variables used in rows and columns, and displaying the other variables unconditioned in each cell of the resulting tabular layout.

 \cite{mackinlay:1986, mackinlay2007}: VisQL, a visual query language is designed to capture the flow of a graphical data exploration.

>>>>

The product plots framework is heavily influenced by the work of WIlkinson \citep{wilkinson:1999, wilkinson:2005}, who introduced the set product operator to map hierarchical data to a two-dimensional framework.  Wilkinson restricts (??? not quite sure - need to lookit up) the use to standard mosaicplots as defined by Hartigan \citep{hartigan:1981}, which could easily be extended, however the product plots framework additionally introduces the concept of conditioning on variables.

@@

The framework of  Polaris  \cite{stolte:2002} relies heavily on a tabular or cubic format in rendering hierarchical graphics, which makes these charts essentially a three dimensional extension of the trellis framework \citep{cleveland:1994,becker:1996}:  in the product plots framework, this approach is captured by conditioning on the variables used in rows and columns, and displaying the other variables unconditioned in each cell of the resulting tabular layout.

 \cite{mackinlay:1986,mackinlay:2007}: VisQL, a visual query language is designed to capture the flow of a graphical data exploration.
